Verification of Stencil Computations through Spatial Specifications

### 2016-07-04 paper.tex
correcting the model and extending the proofs to new equations

\begin{figure}[t]
\begin{align*}
\def\arraystretch{1.2}
\setlength{\arraycolsep}{0.2em}
\newcommand{\dimTy}{\mathbb{D}}
\begin{array}{rl}
\nonterm{specification} ::= & \nonterm{regionDec} \mid \nonterm{specDec} \\
\nonterm{specDec} ::= & \term{stencil} \; \nonterm{specTop} \;
                        \texttt{::} \; v
  \\
\nonterm{regionDec} ::= &  \texttt{region} \; \nonterm{rvar} \; \texttt{=} \;
                         \nonterm{region}\\[1em]
%\nonterm{spec} ::= & \nonterm{spatial} \mid \nonterm{temporal}
%\\[1em]
\nonterm{specTop} ::= & [\nonterm{approxMod},] \; \nonterm{spec} \\
\nonterm{spec} ::= & [\nonterm{multMod},] \; \nonterm{region} \\
\nonterm{multMod} ::= & \term{readOnce} \\
\nonterm{approxMod} ::= & \term{atMost} \; \mid \; \term{atLeast} \\[0.1em]
\nonterm{region} ::= 
        & \stenFwd{\mathbb{N}_{>0}}{\dimTy}{\;[, \texttt{irreflexive}]} \\
\mid \; & \stenBwd{\mathbb{N}_{>0}}{\dimTy}{\;[, \texttt{irreflexive}]} \\
\mid \; & \stenCen{\mathbb{N}_{>0}}{\dimTy}{\;[, \texttt{irreflexive}]} \\
\mid \; & \stenRefl{\dimTy}  \\
\mid \; & \nonterm{region} \; \term{+} \; \nonterm{region} \\
\mid \; & \nonterm{region} \; \term{*} \; \nonterm{region} \\
\mid \; & \nonterm{rvar}  \\[0.5em]
%\nonterm{temporal} ::= \; & \term{dependency} \; (v \; \{ , v \}) [, \texttt{mutual}]
%  \\[0.5em]
\dimTy ::= \; & \mathbb{N}_{>0} \\
\nonterm{rvar} ::= \; & [\text{\term{a}-\term{z}$\,$\term{A}-\term{Z}$\,$\term{0}-\term{9}}]+
\end{array}
\end{align*}
\caption{Specification syntax (EBNF grammar)}
\label{fig:syntax}
\end{figure}

@@

Figure~\ref{fig:equations} lists the equational theory for
specifications which is defined by the binary relation $\equiv$
between region terms. Stencil declarations are considered
equal when they have the same modifiers and $\equiv$ equates
their regions, \ie{}:
\begin{align*}
& \textit{region} \equiv \textit{region'} \\
& \quad \Rightarrow \;\; \texttt{stencil} \; [\textit{approxMod},] \; [\textit{multMod},] \;
\textit{region} \\[-0.4em]
& \quad\quad \;\; \equiv \;\texttt{stencil} \; [\textit{approxMod},] \;
            [\textit{multMod},] \; \textit{region}'
\end{align*}
%
To save space in the equations of Figure~\ref{fig:equations}, we use abbreviations
\term{refl}, \term{fwd}, \term{bwd}, and \term{cen} for \term{reflexive},
\term{forward}, \term{backward}, and \term{centered} regions
respectively. Futhermore, the abbreviations include syntactic sugar
for quantifying over the abseence or presence of the \irrefl{}
attribute on region constants as a boolean. For example, 
the syntactic sugar in our equations for \term{fwd} is defined:
%%
\begin{align*}
& \stenFwdSR{n}{d}{r} 
\; := \; \\[-0.4em]
& \qquad \begin{cases}
\stenFwd{n}{d}{, \irrefl} & \textit{if} \;\, \neg \, r \\
\stenFwd{n}{d}{}  & \textit{if} \;\,  r
\end{cases}
\end{align*}
%
and similarly for \term{bwd} and \term{cen}.
We also frequently abbreviate \irrefl{} to \irreflS{}.

@@

We define the interpretation function $\inter{-}$ overloaded on regions
in Figure~\ref{fig:region-model} and on the top-level of 
a specification \textit{specTop} in
Figure~\ref{fig:spatial-model}. Some
intermediate notations and definitions are used.

@@

>>>>

\begin{figure}[t]
\begin{align*}
\def\arraystretch{1.2}
\setlength{\arraycolsep}{0.2em}
\newcommand{\dimTy}{\mathbb{D}}
\begin{array}{rl}
\nonterm{specification} ::= & \nonterm{regionDec} \mid \nonterm{specDec} \\
\nonterm{specDec} ::= & \term{stencil} \; \nonterm{specTop} \;
                        \texttt{::} \; v
  \\
\nonterm{regionDec} ::= &  \texttt{region} \; \nonterm{rvar} \; \texttt{=} \;
                         \nonterm{region}\\[1em]
%\nonterm{spec} ::= & \nonterm{spatial} \mid \nonterm{temporal}
%\\[1em]
\nonterm{specTop} ::= & [\nonterm{approxMod},] \; \nonterm{spec} \\
\nonterm{spec} ::= & [\nonterm{multMod},] \; \nonterm{region} \\
\nonterm{multMod} ::= & \term{readOnce} \\
\nonterm{approxMod} ::= & \term{atMost} \; \mid \; \term{atLeast} \\[0.1em]
\nonterm{region} ::= & \\
\multicolumn{2}{l}{\qquad\qquad\;\;\; \stenFwd{\mathbb{N}_{>0}}{\dimTy}{\;[, \texttt{irreflexive}]}} \\
\multicolumn{2}{l}{\qquad\qquad \mid \; \stenBwd{\mathbb{N}_{>0}}{\dimTy}{\;[, \texttt{irreflexive}]}} \\
\multicolumn{2}{l}{\qquad\qquad \mid \; \stenCen{\mathbb{N}_{>0}}{\dimTy}{\;[, \texttt{irreflexive}]}} \\
\multicolumn{2}{l}{\qquad\qquad \mid \; \stenRefl{\dimTy}}  \\
\multicolumn{2}{l}{\qquad\qquad \mid \; \nonterm{region} \; \term{+} \; \nonterm{region}} \\
\multicolumn{2}{l}{\qquad\qquad \mid \; \nonterm{region} \; \term{*} \; \nonterm{region}} \\
\multicolumn{2}{l}{\qquad\qquad \mid \; \nonterm{rvar}}  \\[0.5em]
%\nonterm{temporal} ::= \; & \term{dependency} \; (v \; \{ , v \}) [, \texttt{mutual}]
%  \\[0.5em]
\dimTy ::= \; & \mathbb{N}_{>0} \\
\nonterm{rvar} ::= \; & [\text{\term{a}-\term{z}$\,$\term{A}-\term{Z}$\,$\term{0}-\term{9}}]+
\end{array}
\end{align*}
\caption{Specification syntax (EBNF grammar)}
\label{fig:syntax}
\end{figure}

@@

Figure~\ref{fig:equations} lists the equational theory for
specifications which is defined by the binary relation $\equiv$
between region terms. Stencil declarations are considered
equal when they have the same modifiers and $\equiv$ equates
their regions, \ie{}:
\begin{align*}
& \textit{region} \equiv \textit{region'} \\
& \quad \Rightarrow \;\; \texttt{stencil} \; [\textit{approxMod},] \; [\textit{multMod},] \;
\textit{region} \\[-0.4em]
& \quad\quad \;\; \equiv \;\texttt{stencil} \; [\textit{approxMod},] \;
            [\textit{multMod},] \; \textit{region}'
\end{align*}
%
To save space in the equations of Figure~\ref{fig:equations}, we use abbreviations
\term{refl}, \term{fwd}, \term{bwd}, and \term{cen} for \term{reflexive},
\term{forward}, \term{backward}, and \term{centered} regions
respectively. Futhermore, the abbreviations include syntactic sugar
for quantifying over the abseence or presence of the \irrefl{}
attribute on region constants as a boolean. For example, 
the syntactic sugar in our equations for \term{fwd} is defined:
%%
\begin{align*}
& \stenFwdSR{n}{d}{r} 
\; := \; \\[-0.4em]
& \qquad \begin{cases}
\stenFwd{n}{d}{, \irrefl} & \textit{if} \;\, \neg \, r \\
\stenFwd{n}{d}{}  & \textit{if} \;\,  r
\end{cases} \\
\textit{or} \;\;
& \stenFwdS{n}{d} := \stenFwd{n}{d}{}
\end{align*}
%
and similarly for \term{bwd} and \term{cen}.
We also frequently abbreviate \irrefl{} to \irreflS{}.

@@

We define the interpretation function $\interp{-}_n$ where $n$ is the
maximum dimensionality of the specification being modelled, overloaded
on regions in Figure~\ref{fig:region-model} and on the top-level of a
specification \textit{specTop} in Figure~\ref{fig:spatial-model}. Some
intermediate notations and definitions are used.

@@

The first four equations of Figure~\ref{fig:region-model}
give the meanings of the region constants as sets of indices.
